Generalized Plackett-Luce Likelihoods

### 2022-09-25 inst/surfing_jsa_rebuttal_minorcomments.tex

\documentclass[12pt]{article}
\usepackage{xcolor}
\begin{document}

\section*{MS596 ``Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods": response to minor comments}

Below, we reproduce the two reviewers' minor comments; our replies to
the issues are in \textcolor{blue}{blue}.  We have indicated changes
to the manuscript where appropriate.

Short story: each of the  comments is perfectly reasonable and we have 
changed the manuscript as suggested.

\subsection*{placeholder comment}

Foo should be bar

\textcolor{blue}{generic placeholder response}

\end{document}

### 2022-09-25 inst/jss_hyper3.Rnw

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.  The package
includes an \proglang{S3} class \code{hyper3} for this type of object;
extraction and replacement methods use \pkg{disordR}
discipline~\citep{hankin2022}.  Package idiom for creating such
objects uses named vectors:

@@

Above, we see object \code{LL} is a log-likelihood function of the
players' strengths, which may be evaluated at specified points in
probability space.  If, for example, we wish to assess $H_1\colon
p_a=0.9,p_b=0.05,p_c=0.05$ and $H_2\colon p_a=0.01,p_b=0.01,p_c=0.98$,
we can evaluate these hypotheses using generic function
\code{loglik()}:

@@

We may find a maximum likelihood estimate for the players' strengths,
using generic function \code{maxp()}:

@@

>>>>

Above, object \code{L} is an object of class \code{hyper3}; it may be
evaluated at points in probability space [that is, a vector
\code{[a,b,c]} of nonnegative values with unit sum] using standard
\proglang{R} idiom wrapping \proglang{C++} back end.

\subsection{Package implementation}

The package includes an \proglang{S3} class \code{hyper3} for this
type of object; extraction and replacement methods use \pkg{disordR}
discipline~\citep{hankin2022}.  Package idiom for creating such
objects uses named vectors:

@@

Above, we see object \code{LL} is a log-likelihood function of the
players' strengths, which may be evaluated at specified points in
probability space.  A typical use-case would be to assess $H_1\colon
p_a=0.9,p_b=0.05,p_c=0.05$ and $H_2\colon p_a=0.01,p_b=0.01,p_c=0.98$,
we can evaluate these hypotheses using generic function
\code{loglik()}:

@@

We may find a maximum likelihood estimate for the players' strengths,
using generic function \code{maxp()}, dispatching to a specialist
\code{hyper3} method:

@@

\code{Package helper functions}

Arithmetic operations are implemented for \code{hyper3} objects in
much the same way as for \code{hyper2} objects: independent
observations may be combined using the overloaded \code{+} operator;
an example is given below.

The original motivation for \code{hyper3} was the analysis of Formula
1 motor racing, and the package accordingly includes wrappers for
\code{ordervec2supp()} such as \code{ordertable2supp3()} and
\code{attemptstable2supp3()} which facilitate the analysis of commonly
encountered result formats; an example is given below.
